A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-25 paper/main.tex
Fix manuscript to build again
fix reference.bib

\todo{where from, or how created?}

@@

% Discussion
% words > no-speech
For the contrast words > no-speech, we find increased hemodynamic activity in a
bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
Our results are similar to results of studies that implemented an ISC approach
to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
lerner2011topographic, silbert2014coupled, wilson2007beyond}.
% dissimilarities
\todo{Which contrast captures ANY social aspects? CH: the COPEs in the
references} Contrary to previous studies \citep{ferstl2008extended,
mar2011neural}, we do not find increased medial activation in the precuneus or
medial frontal cortex. This could be attributed to the fact that the contrast
here was not designed to capture social aspects of the
narrative.\todo{wilson2007beyond: ISC medial ja, aber decreased activation
    compared to rest; current study in reverse contrast: posterior cingulate and
anterior cingulate (and insula bilaterally)}.
% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions yielded increased activation that is partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the exploratory nature of our analysis. A high count
of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
huth2016natural}), and contrasted to coordinate conjunctions that offered a
comparably small amount of events (N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Coordinate junctions were chosen because they were assumed to be temporally
uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
``but'' (N=49), and thus offered only a small amount of variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately \unit[70]{ms} lasting events in quick succession did
not capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask:
    If you knew all these issues, why did you do it then? hindsight bias/HARKing
after exploratory analyses?!}.
% but...
Nevertheless and more importantly to exploratorily access the validity of the
dataset is the fact that two similar linguistic concepts (nouns and proper
nouns) embedded in a naturalistic stimulus that was not designed for linguistic
research lead to similar activation patterns\todo{That statement is only true,
if both contrasts are not (solely) driven by the conjunctions. There is no
evidence in the paper that this is not the case.}
% Within the language processing systems, early sensory regions are specialized
% for representing the immediate physical properties of the environment (form),
% while higher order regions extract increasingly abstract content (Davis and
% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).

>>>>

\todo[inline]{where from, or how created?}

@@

% Discussion
% words > no-speech
For the contrast words > no-speech, we find increased hemodynamic activity in a
bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
Our results are similar to results of studies that implemented an ISC approach
to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
lerner2011topographic, silbert2014coupled, wilson2008beyond}.
% dissimilarities
\todo{Which contrast captures ANY social aspects? CH: the COPEs in the
references} Contrary to previous studies \citep{ferstl2008extended,
mar2011neural}, we do not find increased medial activation in the precuneus or
medial frontal cortex. This could be attributed to the fact that the contrast
here was not designed to capture social aspects of the
narrative.\todo{wilson2007beyond: ISC medial ja, aber decreased activation
    compared to rest; current study in reverse contrast: posterior cingulate and
anterior cingulate (and insula bilaterally)}.
% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions yielded increased activation that is partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the exploratory nature of our analysis. A high count
of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
huth2016natural}), and contrasted to coordinate conjunctions that offered a
comparably small amount of events (N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Coordinate junctions were chosen because they were assumed to be temporally
uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
``but'' (N=49), and thus offered only a small amount of variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately \unit[70]{ms} lasting events in quick succession did
not capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask:
    If you knew all these issues, why did you do it then? hindsight bias/HARKing
after exploratory analyses?!}.
% but...
Nevertheless and more importantly to exploratorily access the validity of the
dataset is the fact that two similar linguistic concepts (nouns and proper
nouns) embedded in a naturalistic stimulus that was not designed for linguistic
research lead to similar activation patterns\todo{That statement is only true,
if both contrasts are not (solely) driven by the conjunctions. There is no
evidence in the paper that this is not the case.}
% Within the language processing systems, early sensory regions are specialized
% for representing the immediate physical properties of the environment (form),
% while higher order regions extract increasingly abstract content (Davis and
% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).
